\subsection{The Higgs Boson}

One additional particle that plays a significant role in the \gls{sm} is the Higgs boson. Unlike the other bosons,
which mediate the fundamental forces, the Higgs boson is associated with the Higgs field, a scalar field that permeates
all space. The Higgs boson was proposed in 1964 by physicist Peter Higgs and others as a result of their work on the
so-called "Higgs mechanism" \cite{higgs}.

The Higgs mechanism is responsible for the mass of elementary particles. According to this theory, particles acquire
mass by interacting with the Higgs field. The more strongly a particle interacts with this field, the greater its mass.
Particles that do not interact with the Higgs field, such as photons, are massless.

The existence of the Higgs boson and the Higgs field was confirmed experimentally in 2012 by the \gls{atlas} and \gls{cms}
collaborations at \gls{cern}\footnote{\url{https://atlas.cern/updates/feature/higgs-boson}}, a discovery that led to the
awarding of the 2013 Nobel Prize in Physics to François Englert and Peter Higgs.

The Higgs boson itself is unstable and quickly decays into other particles. The decay channels and their corresponding
probabilities, or branching ratios, are predicted by the \gls{sm}. One particular decay of interest in
this work is the Higgs decay into a tau lepton pair, denoted as $H \rightarrow \tau\bar{\tau}$, which has a branching
ratio of approximately 6\% (\autoref{fig:higgs-decays}).

\begin{table}[htb]
    \centering
    \label{tab:higgs-decays}
    \renewcommand{\arraystretch}{1.5}
    \begin{tabular}{l@{\hspace{1cm}}c@{\hspace{1cm}}c}
        \toprule
        Decay Channel                & Branching Ratio       & Relative Uncertainty \\
        \midrule
        $H \rightarrow \gamma\gamma$ & $2.28 \times 10^{-3}$ & $^{+5.0\%}_{-4.9\%}$ \\
        $H \rightarrow ZZ$           & $2.64 \times 10^{-2}$ & $^{+4.3\%}_{-4.1\%}$ \\
        $H \rightarrow W^+W^-$       & $2.15 \times 10^{-1}$ & $^{+4.3\%}_{-4.2\%}$ \\
        $H \rightarrow \tau^+\tau^-$ & $6.32 \times 10^{-2}$ & $^{+5.7\%}_{-5.7\%}$ \\
        $H \rightarrow b\bar{b}$     & $5.77 \times 10^{-1}$ & $^{+3.2\%}_{-3.3\%}$ \\
        $H \rightarrow Z\gamma$      & $1.54 \times 10^{-3}$ & $^{+9.0\%}_{-8.9\%}$ \\
        $H \rightarrow \mu^+\mu^-$   & $2.19 \times 10^{-4}$ & $^{+6.0\%}_{-5.9\%}$ \\
        \bottomrule
    \end{tabular}
    \vspace{5pt}
    \caption[Branching ratios for various Higgs boson decay channels]
    {Branching ratios for various Higgs boson decay channels. Taken from
        \url{http://opendata.atlas.cern/books/current/get-started/_book/the-higgs-boson.html}}
    \label{fig:higgs-decays}
\end{table}
