\chapter{Evaluating Classifier Performance and Estimating Significance and Uncertainties}

In this chapter, we will delve into the application of our trained neural network classifier to our data set, with the
aim of separating the signal (\ttH process) from the background. We will discuss the process of defining a signal region
based on the classifier scores, and how this region is optimized to maximize the sensitivity of our analysis to the
signal process.

We will then move on to the calculation of the significance of our signal. This will involve comparing the number of
observed events in our signal region to the number of expected background events, and calculating the probability that
any observed excess could have occurred by chance under the null hypothesis. We will present the formulas used for this
calculation, and discuss their assumptions and limitations.

Next, we will discuss the estimation of uncertainties. We will differentiate between statistical uncertainties, which
arise from the random nature of the data and can be reduced by collecting more data, and systematic uncertainties, which
arise from limitations in our understanding or modeling of the experiment. We will present methods for estimating these
uncertainties and discuss how they affect our results.

Finally, we will present the results of our analysis, including the estimated significance and uncertainties, and
discuss their implications. We will also discuss potential improvements and future directions for this work.

This chapter will provide a comprehensive overview of how a trained classifier is applied to real data and how its
performance is evaluated in terms of sensitivity, significance, and uncertainties. It will provide a practical guide to
the statistical methods used in particle physics analyses, and demonstrate their application to our specific case of the
\ttH process.

\input{chapters/4-evaluation/1-regions.tex}
\input{chapters/4-evaluation/2-significance.tex}
\input{chapters/4-evaluation/3-uncertainties.tex}