\chapter*{Acknowledgements}
\addcontentsline{toc}{chapter}{Acknowledgements}

I wish to express my profound gratitude to the following individuals, whose invaluable contributions were indispensable
in the realization of this thesis:

Firstly, I would like to offer my deepest thanks to my supervisor, doc. Dr. Andr\'{e}\: Sopczak. His consistent
guidance, valuable insights, and steadfast support were integral throughout the course of this research. His scholarly
wisdom and continuous encouragement have been pivotal in my academic journey.

My sincere appreciation extends to the remarkable CERN community. Their relentless support, coupled with their
readiness to offer assistance, helped me overcome many challenges. My experience as a part of this esteemed
organization has been life-changing, and I am incredibly grateful for the opportunity.

I owe a debt of gratitude to Luca Martinelli, Martin Vatrt, and Nihal Brahimi. Their mentorship and patient elucidation
of complex physical and technical principles have proven invaluable. Their generosity in sharing their expertise is
deeply appreciated, as are the numerous hours they dedicated to answering my relentless inquiries.

My heartfelt thanks go to my dear friend, Andrii, whose expertise in machine learning was instrumental in resolving
several complex issues. His assistance and eagerness to aid me were indispensable in implementing advanced techniques
for this research.

To my beloved partner, Anna, I express my eternal gratitude. Her unwavering support, understanding, and encouragement
have been my constant source of strength and inspiration during this journey.

Lastly, my deepest appreciation goes to all my friends and family. Their faith in my capabilities and their constant
encouragement have fueled my pursuit of this academic endeavor.

Each person named above has played an instrumental role in shaping this thesis, and I am profoundly grateful for their
influence in my life. Their collective support has been a beacon throughout this challenging yet rewarding academic
journey. My sincerest thanks to you all.

In closing, I wish to pay tribute to the brave men and women of the Ukrainian armed forces for their unwavering
commitment and sacrifice in safeguarding our homeland during times of conflict. Their courage and selflessness in
adversity are protecting our nation's sovereignty and ensuring the safety of our citizens. The sacrifices made by these
brave individuals and their families resonate deeply within me. Their service is a testament to the spirit of our nation
and is held in the utmost esteem. I am profoundly proud to call Ukraine my homeland and I am honored to acknowledge the
indelible contributions of our armed forces in defending our shared values and freedoms.  Your service and commitment to
protecting our nation will forever be respected and cherished.